### 2020-10-10 README.Rmd
everything runs!

For SCBI we will just look at a 16 ha plot to speed calculations.

```{r, eval = run_scbi}
# SCBI
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>%
  mutate(date = mdy(date)) %>%
  filter(gy <= 400)

scbi_2018 <-
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem3.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>% 
  mutate(dbh = as.numeric(dbh),
         date = mdy(date)) %>%
  filter(gy <= 400)
```

@@

```{r, eval = run_scbi}
# SCBI
# Study region boundary polygon
scbi_study_region <- 
 #tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  tibble(x = c(0,400,400,0,0), y = c(0,0,400,400,0)) %>% 
  sf_polygon()

@@

```{r, eval = run_scbi}
# SCBI
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 20, yOffset = 0.9999, verbose = FALSE
)

@@

```{r, eval = run_scbi}
# SCBI
scbi_growth_df <- focal_vs_comp_scbi %>% 
  predict_bayesian_model(posterior_param = posterior_param_scbi) %>% 
  right_join(scbi_growth_df, by = c("focal_ID" = "stemID"))

# Observed vs predicted growth  
ggplot(scbi_growth_df, aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0, 0, 0, 0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh", 
    title = "Predicted vs Observed Growth"
  )

reslab <- expression(paste('Residual (cm ',y^{-1},')'))
scbi_growth_df %>% 
  st_as_sf() %>%
  # Need to investigate missingness
  filter(!is.na(growth_hat)) %>% 
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5), 
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>% 
  ggplot() + 
  geom_sf(aes(col = error_compress), size = 0.4) + 
  theme_bw() + 
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf", 
    name = reslab,
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c('< -0.75', '-0.5', '0.25', '0', '0.25', '0.5', '> 0.75')) +
  labs(x = "Meter", y = "Meter")
```

@@

```{r, eval = FALSE}
# SCBI
tic()
cv_scbi <- focal_vs_comp_scbi %>%
  run_cv(max_dist = max_dist, cv_grid = scbi_cv_grid) %>%
  right_join(scbi_growth_df, by = c("focal_ID" = "treeID"))
toc()

@@

```{r, eval = run_scbi}
posterior_plots_scbi[["lambda"]]
#comment to change
```

>>>>

For SCBI we will just look at a 9 ha plot to speed calculations.

```{r, eval = run_scbi}
# SCBI
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>%
  mutate(date = mdy(date)) %>%
  filter(gx < 300, gy > 300, gy < 600)

scbi_2018 <-
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem3.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>% 
  mutate(dbh = as.numeric(dbh),
         date = mdy(date))  %>%
  filter(gx < 300, gy > 300, gy < 600)
```

@@

```{r, eval = run_scbi}
# SCBI
# Study region boundary polygon
scbi_study_region <- 
 #tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  tibble(x = c(0,300,300,0,0), y = c(300,300,600,600,3)) %>% 
  sf_polygon()

@@

```{r, eval = run_scbi}
# SCBI
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, yOffset = 0.9999, k = 9, verbose = FALSE
)

@@

```{r, eval = run_scbi}
# SCBI
scbi_growth_df_noCV <- focal_vs_comp_scbi %>% 
  predict_bayesian_model(posterior_param = posterior_param_scbi) %>% 
  right_join(scbi_growth_df, by = c("focal_ID" = "stemID"))

# Observed vs predicted growth  
ggplot(scbi_growth_df_noCV, aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0, 0, 0, 0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh", 
    title = "Predicted vs Observed Growth"
  )

reslab <- expression(paste('Residual (cm ',y^{-1},')'))
scbi_growth_df_noCV %>% 
  st_as_sf() %>%
  # Need to investigate missingness
  filter(!is.na(growth_hat)) %>% 
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5), 
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>% 
  ggplot() + 
  geom_sf(aes(col = error_compress), size = 1) + 
  theme_bw() + 
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf", 
    name = reslab,
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c('< -0.75', '-0.5', '0.25', '0', '0.25', '0.5', '> 0.75')) +
  labs(x = "Meter", y = "Meter")
```

@@

```{r, eval = run_scbi}
# SCBI
tic()
cv_scbi <- focal_vs_comp_scbi %>%
  run_cv(max_dist = max_dist, cv_grid = scbi_cv_grid) %>%
  right_join(scbi_growth_df, by = c("focal_ID" = "treeID"))
toc()

@@

```{r, eval = run_scbi}
posterior_plots_scbi[["lambda"]]
```
